---
title: "SAS Project"
author: "Abhishek Singh (17251693)"
date: "18 April 2018"
output:
  pdf_document: default
  html_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## R Markdown

### Reading the data
```{r}
data <- read.csv("C:/Users/solab/OneDrive/Documents/Data_Science_Notes/Topics_Data_Analytics/MUSUrvey.csv", header=T, row.names=1, na.strings = c(""))
pairs(data)
```

###View missing and unique values
```{r}
sapply(data,function(x) sum(is.na(x)))
sapply(data, function(x) length(unique(x)))
library(Amelia)
missmap(data, main = "Missing values vs observed")
```

###Treating the NA values. Replacing the numeric variables with their mean values.
```{r}
data$Hours[is.na(data$Hours)] <- mean(data$Hours, na.rm=T)
data$Societies[is.na(data$Societies)] <- mean(data$Societies, na.rm=T)
```

###Since not able to treat categorical variables therefore discarding it.
###Discarding the row
```{r}
data <- data[!is.na(data$CYr),]
data <- data[!is.na(data$Dept),]
data <- data[!is.na(data$ExtraH),]
data <- data[!is.na(data$CG),]
data <- data[!is.na(data$EG),]
data <- data[!is.na(data$Travel),]
```

### Finding the best subset model
```{r}
library(leaps)
best.subset <- regsubsets(EG ~ CYr+Dept+Hours+ExtraH+CG+Travel+Work+Societies+Party,
           data = data,
           nbest = 1,       # 1 best model for each number of predictors
           nvmax = NULL,    # NULL for no limit on number of variables
           force.in = NULL, force.out = NULL,
           method = "exhaustive")
best.subset
summary.out <- summary(best.subset)
as.data.frame(summary.out$outmat)

```


###It'll show how many predictors are good in model including the factors of variables.
```{r}
which.max(summary.out$adjr2)
```

###Viewing the predictors for best subset model
```{r}

summary.out$which[15,]
```

###Best predictors came out to be are CYr, Dept, ExtraH, CG, Travel, Work, Party
###Thus, selecting only these predictors
```{r}
best.subset.data <- within(data, {
  #CYr   <- NULL         # Delete
  #Dept  <- NULL
  Hours <- NULL
  #ExtraH  <- NULL
  #CG  <- NULL
  #EG <- NULL
  #Travel  <- NULL
  #Work  <- NULL
  Societies  <- NULL
  #Party  <- NULL
  Arts  <- NULL
  EStudy  <- NULL
  CG1  <- NULL
  EG1  <- NULL
})
```

###Dividing the data between training and test
```{r}

library(nnet) 
alpha<-0.7
d <- sort(sample(nrow(best.subset.data), nrow(best.subset.data)*alpha))
train <- best.subset.data[d,]
test <- best.subset.data[-d,]
```

###Fitting logistic regression
```{r}

model <- multinom(EG ~ ., data=train)
summary(model)
fitted.results <- predict(model, test, "probs")
```

###Assigning probability value greater than 0.5 as 1 else 0. It'll also replace NANs with 0 as they are nothing but value close to 0.
```{r}

fitted.results <- ifelse(fitted.results < 0.5, 0, 1)
head(fitted.results)
```

###Converting the dummy values of fitted.results and test$EG into "a", "b", "c" and "d" levels, so that accuracy can be calculated.
```{r}
pred.EG <- 0
for(i in 1:nrow(fitted.results)) {
  pred.EG[i] <- ifelse(fitted.results[i,1] == 1, "a",
                ifelse(fitted.results[i,2] == 1, "b",
                  ifelse(fitted.results[i,3] == 1, "c", "d")))
            }


expected.EG <- ifelse(test$EG == 1.1, "a",
                ifelse(test$EG == 2.1, "b",
                  ifelse(test$EG == 2.2, "c", "d")))

EG.table = table("Expected Value"=expected.EG, 'Predicted value'= pred.EG)
prop.table(EG.table)
misClasificError <- mean(pred.EG != expected.EG)
print(paste('Accuracy', (1-mean(pred.EG != expected.EG))))
```

# Performing another logistic regression for Predicting the department of students.
```{r}
sas1 <- read.csv("C:/Users/solab/OneDrive/Documents/Data_Science_Notes/Topics_Data_Analytics/MUSUrvey.csv", header=T, row.names=1, na.strings = c(""))

```

###Treating the NA values. Replacing the numeric variables with their mean values.
###Since not able to treat categorical variables therefore discarding it.
###Discarding the row
```{r}
sapply(sas1,function(x) sum(is.na(x)))
sas1$Hours[is.na(sas1$Hours)] <- mean(sas1$Hours, na.rm=T)
sas1$Societies[is.na(sas1$Societies)] <- mean(sas1$Societies, na.rm=T)
sapply(sas1,function(x) sum(is.na(x)))
```

###Fitting the model
```{r}
f = glm(Arts~Hours+EStudy+CG1+Societies+Party, family = "binomial", data=sas1)
summary(f)
```

###Assigning probability values greater than 0.5 as 1 or else 0.
```{r}
prob = predict(f, type="response")
pred = factor(ifelse(prob <= .5, "No","Yes"))

```

###Calculating the error
```{r}
tab1=table(pred, sas1$Arts)
tab1
er1 = ((tab1[2,1]+tab1[1,2])/sum(tab1))*100
er1
```

